Final Project

### 2025-04-24 MSSC5750_Project.qmd
Add files via upload

```{r echo = FALSE, message=FALSE}
library(MASS)
library(ggplot2)
library(dplyr)
library(scales)

@@

>>>>

```{r echo = FALSE, message=FALSE}
library(MASS)
library(ggplot2)
library(dplyr)
library(scales)
library(glmnet)
library(fastDummies)
library(caret)

@@

 Outline for LASSO regression to help with variable selection
```{R}

# One-hot-encoding our categorical variables. Should happen automatically for factors
data$person_gender <- as.factor(data$person_gender)
data$person_home_ownership<-as.factor(data$person_home_ownership)
data$loan_intent<-as.factor(data$loan_intent)
data$previous_loan_defaults_on_file<-as.factor(data$previous_loan_defaults_on_file)

# Extracting outcome variable
class <- data$loan_status

# Converting to a matrix
matrixData <- model.matrix(class ~ ., data = data %>% select(-loan_status))

# First column is all intercepts
matrixData<- matrixData[,-1]

# Uses cross validation, no need to train/test split. Alpha selects lasso (rather than ridge regression), but I think thats the default anyways
lasso <- cv.glmnet(matrixData, class, alpha = 1, family = "binomial")

# See coefficients, which variables we might drop
coef(lasso)

# Make predictions
data$lassoPred <- as.vector(predict(lasso, newx = matrixData, type = "class"))

# Evaluate accuracy measures
confusionMatrix(factor(data$lassoPred), factor(data$loan_status), positive = '1')
